Verifying Demonstrations

### 2019-02-15 paper/system-model.tex
Emphasizes relation to petitions

We note that, in general terms, protesting is very similar to petitions, which 
in turn are similar to voting.
Indeed, all three situations correspond to situations in which many individuals express their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.

>>>>

We note that, in general terms, protests are petitions with a given time and 
location.
Protests, petitions and elections share that in all three many individuals 
express their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or 
persecution).
For that reason we have strong requirements for verification and privacy for 
elections, it follows that we should have similar properties for protests
and petitions.
